The Concurrent Calculi Formalisation Benchmark

### 2024-02-22 short-paper/short-paper.tex
Minor edits in coinduction section.

While many proof assistants support coinductive techniques, they do so
through subtly different formalisms, enabling various
approaches. Additionally, some systems offer multiple abstractions for
utilising coinduction. Examples are Agda's musical notation versus  co-patterns and sized types~\cite{Abel2013}. In Coq, guarded recursion versus a refined fixed point approach as supported by the parameterised coinduction~\cite{Hur2013}
and interaction tree~\cite{Xia2019} libraries.

When reasoning over bisimilarity many authors rely on the native
 coinduction offered by the chosen proof assistants
\cite{Bengtson2016,Kahsai2008,Thiemann2019,Gay2020}, others prefer a
more ``set-theoretic'' approach
\cite{Hirschkoff1997,Bengtson2009,Maksimovic2015,Pohjola2022}. Some
use both and establish an internal adequacy~\cite{Honsell2001}. Few
extend the proof assistant foundations to allow \eg reasoning about
bisimilarity up-to~\cite{ChaudhuriCM15}.

>>>>

While many proof assistants support coinductive techniques, they do so
through subtly different formalisms, enabling various approaches.
Additionally, some systems offer multiple abstractions for utilising coinduction.
For instance, Agda offers musical notation, co-patterns and sized types~\cite{Abel2013};
Coq offers guarded recursion and refined fixed point approaches as supported by the parameterised coinduction~\cite{Hur2013}
and interaction tree~\cite{Xia2019} libraries.

When reasoning over bisimilarity many authors rely on the native
 coinduction offered by the chosen proof assistants
\cite{Bengtson2016,Kahsai2008,Thiemann2019,Gay2020}, while others prefer a
more ``set-theoretic'' approach
\cite{Hirschkoff1997,Bengtson2009,Maksimovic2015,Pohjola2022}. Some
use both and establish an internal adequacy~\cite{Honsell2001}. Few
extend the proof assistant foundations to allow \eg reasoning about
bisimilarity up-to~\cite{ChaudhuriCM15}.
